Borel regularity for ODEs and exponential integrals

### 2023-03-15 exp-resurgence.tex
updates

\textcolor{lime}{[Use Poincar\'e algorithm to compute the asymptotic expansion]}

@@

%\subsection{Going to the spatial domain}\label{spatial-AL}
\subsubsection{The big idea}\label{big-idea}
We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}. We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.

@@

We define the following exponential integral: let $p\geq 0$, $f(t)=\tfrac{t^3}{3}-t$ and $\nu_p=\tfrac{dt}{t^p}$. The critical points of $f$ are $\pm\tfrac{2}{3}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic

\begin{equation}
I_\alpha(z,p)\defeq\frac{1}{2\pi i}\int_{\mathcal{C}_{\alpha}}e^{-z(\tfrac{t^3}{3}-t)}\frac{dt}{t^p}
\end{equation}

where $\mathcal{C}_\alpha$ is the path through the point $\alpha$, starting and ending at infinity (as in Figure \ref{fig:path for I}). In particular, $I_{+}(z,p)=z^{\tfrac{p-1}{3}}\mathrm{A}_1(z^{2/3},p)$:

\begin{align*}
I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\mathcal{C}_{+}}e^{-z(\tfrac{t^3}{3}-t)}\frac{dt}{t^p} &\\
&=\frac{z^{(p-1)/2}}{2\pi i}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-z(z^{-1}\tfrac{s^3}{3}-z^{-1/3}s)}\frac{ds}{s^p} & t=z^{-\tfrac{1}{3}}s\\
&=\frac{z^{(p-1)/3}}{2\pi i}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-\left(\tfrac{s^3}{3}-z^{2/3}s\right)}\frac{ds}{s^p} & \\
&=z^{(p-1)/3}\mathrm{A}_1(z^{2/3},p)
\end{align*}

@@

\begin{equation}\label{eq:I}
\left[\partial_z^3-\frac{4}{9}\partial_z+\frac{2-p}{z}\partial_z^2-\frac{4(1-p)}{9z}-\frac{1+3p-3p^2}{9}\frac{\partial_z}{z^2}+\frac{3+p-3p^2-p^3}{27z^3}\right]I_+(z,p)=0
\end{equation}

From the general theory of linear ODE, the formal integral solution of \eqref{eq:I} is a linear combinations of three generators 
\begin{equation}
\tilde{I}_+(z,p)=U_1z^{p-1}\tilde{W}_1(z)+U_2e^{-\tfrac{2}{3}z}z^{-1/2}\tilde{W}_2(z)+U_3e^{\tfrac{2}{3}z}z^{-1/2}\tilde{W}_3(z)
\end{equation}

@@

\begin{multline}\label{w1}
\left[\partial_z^3-\frac{4}{9}\partial_z-\frac{1-2p}{z}\partial_z^2+\frac{17-30p+12p^2}{9z^2}\partial_z+\frac{8}{27}\frac{p^3-6p^2+11p-6}{z^3}\right]\tilde{W}_1(z)=0
\end{multline}

\begin{multline}\label{w2}
\left[\partial_z^3-2\partial_z^2+\frac{8}{9}\partial_z+\frac{1-2p}{2z}\partial_z^2-\frac{2-4p}{3z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
\left.-\frac{5+24p+12p^2}{54z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_2(z)=0
\end{multline}

\begin{multline}\label{w3}
\left[\partial_z^3+2\partial_z^2+\frac{8}{9}\partial_z+\frac{1-2p}{2z}\partial_z^2+\frac{2-4p}{3z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
\left.+\frac{5+24p+12p^2}{54z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_3(z)=0
\end{multline}
Let us first study equation \eqref{w1}: its Borel transform is

\begin{multline*}
-\zeta^3\tilde{w}_1+\frac{4}{9}\zeta\tilde{w}_1-(1-2p)\int_0^\zeta\tilde{w}_1(t)t^2dt+\frac{(17-30p+12p^2)}{9}\int_0^\zeta(-t\tilde{w}_1(t))(\zeta-t)dt+\\
+\frac{8}{27}(p^3-6p^2+11p-6)\int_0^\zeta\tilde{w}_1(t)\frac{(\zeta-t)^2}{2}dt=0
\end{multline*}

@@

\begin{multline*}
\left(\frac{4}{9}\zeta-\zeta^3\right)\tilde{w}_1^{(3)}(\zeta)+\left(\frac{4}{3}-2(5-p)\zeta^2\right)\tilde{w}_1''(\zeta)-\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\tilde{w}_1'(\zeta)+\\
+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\tilde{w}_1(\zeta)=0
\end{multline*}

we set $y=\tfrac{9}{4}\zeta^2$

%\begin{multline}
%\left[-4y(y-1)(2y\partial_y^3+3\partial_y^2)+3(4y\partial_y^2+2\partial_y)-2(5-p)y(4y\partial_y^2+2\partial_y)+\right.\\
%\left.-2y\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\partial_y+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\right]\tilde{w}_1(y)=0
%\end{multline}
\begin{multline}\label{eq:hw1}
y^2(1-y)\tilde{w}_1^{(3)}(y)+y\left(\left(p-\frac{13}{2}\right)y+3\right)\tilde{w}_1''(y)-\left(y\left(\frac{305}{36}-\frac{1}{3}(10-p)p\right)-\frac{3}{4}\right)\tilde{w}_1'(y)+\\
+\frac{1}{27}\left(p-\frac{5}{2}\right)\tilde{w}_1(y)=0
\end{multline}

@@

therefore, $\tilde{w}_1(y)=c_1\,\,{}_3F_2\left(\mathbf{a}_0;\mathbf{b}_0;y\right)+R(\zeta)$ for some function $R(\zeta)$ which can be determined from the integral equation.

@@

\begin{multline}
-\zeta^3\tilde{w}_2(\zeta)-2\zeta^2\tilde{w}_2(\zeta)-\frac{8}{9}\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt-\frac{2-4p}{3}\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
+\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
-\frac{5+24p+12p^2}{54}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
-\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
\end{multline}

@@

\begin{multline}
\left[\left(\zeta^3+2\zeta^2+\frac{8}{9}\zeta\right)\partial_\zeta^3 +\frac{8}{3}\partial_\zeta^2+\left(\frac{17}{2}+p\right)\zeta\left(\zeta+\frac{4}{3}\right)\partial_\zeta^2+\right.\\
\left. \left(\frac{p^2}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(\zeta+\frac{2}{3}\right)\partial_\zeta+\frac{1}{27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(\zeta)=0
\end{multline}

@@

\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q_1\big(\tfrac{\partial}{\partial z}\big) + z^{-2} Q_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} Q_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
where $Q_k$ has degree $n-k$. \textcolor{gray}{has to be done}

@@

The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
which seem analogous to the trans-monomials above. Borel summation makes the analogy precise. We will see in Section~\ref{bessel-regularity} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$. This is an evidence of Theorem~\ref{thm:1}

>>>>

@@

From the general theory of ODE of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel-AL} has a basis of trans-monomials
\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$ and $\tau_\alpha=1/2$. From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
\begin{equation}\label{bessel-asymp-AL}
\series{W}_1 = 1 - \frac{(\tfrac{1}{2}-\tfrac{m}{n})_1 (\tfrac{1}{2}+\frac{m}{n})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{2}-\tfrac{m}{n})_2 (\tfrac{1}{2}+\tfrac{m}{n})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{2}+\tfrac{m}{n})_3 (\tfrac{1}{2}+\tfrac{m}{n})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
\end{equation}

The holomorphic analysis in Section~\ref{big-idea} will give us holomorphic solutions
\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
which seem analogous to the trans-monomials above. Borel summation makes the analogy precise. We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$. This is an evidence of Theorem~\ref{thm:1}.
%\subsection{Going to the spatial domain}\label{spatial-AL}
\subsubsection{The big idea}\label{big-idea}
We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}. We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.

@@

We define the following exponential integral: let $p\geq 0$, $f(t)=4t^3-3t$ and $\nu_p=\tfrac{dt}{t^p}$. The critical points of $f$ are $\pm\tfrac{1}{2}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic

\begin{equation}
I_\alpha(z,p)\defeq\frac{1}{2\pi i}\int_{\mathcal{C}_{\alpha}}e^{-z(4t^3-3t)}\frac{dt}{t^p}
\end{equation}

where $\mathcal{C}_\alpha$ is the path through the point $\alpha$, starting and ending at infinity (as in Figure \ref{fig:path for I}). In particular, $I_{+}(z,p)=(12 z)^{\tfrac{p-1}{3}}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)$:

\begin{align*}
I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\mathcal{C}_{+}}e^{-z(4t^3-3t)}\frac{dt}{t^p} &\\
&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-z(z^{-1}\frac{s^3}{3}-3 (12 z)^{-1/3}s)}\frac{ds}{s^p} & t=(12 z)^{-\tfrac{1}{3}}s\\
&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-\left(\frac{s^3}{3}-(\tfrac{3}{2} z)^{2/3}s\right)}\frac{ds}{s^p} & \\
&=(12 z)^{(p-1)/3}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)
\end{align*}

@@

\begin{equation}\label{eq:I}
\left[\partial_z^3-\partial_z+\frac{2-p}{z}\partial_z^2+\frac{p-1}{z}+\frac{-1-3p+3p^2}{9}\frac{\partial_z}{z^2}+\frac{3+p-3p^2-p^3}{27z^3}\right]I_+(z,p)=0
\end{equation}

From the general theory of linear ODE, the formal integral solution of \eqref{eq:I} is a linear combinations of three generators 
\begin{equation}
\tilde{I}_+(z,p)=U_1z^{p-1}\tilde{W}_1(z)+U_2e^{-z}z^{-1/2}\tilde{W}_2(z)+U_3e^{z}z^{-1/2}\tilde{W}_3(z)
\end{equation}

@@

\begin{multline}\label{w1}
\left[\partial_z^3-\partial_z-\frac{1-2p}{z}\partial_z^2+\frac{17-30p+12p^2}{9z^2}\partial_z+\frac{8}{27}\frac{p^3-6 p^2+ 11p- 6}{z^3}\right]\tilde{W}_1(z)=0
\end{multline}

\begin{multline}\label{w2}
\left[\partial_z^3-3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2-\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
\left.-\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_2(z)=0
\end{multline}

\begin{multline}\label{w3}
\left[\partial_z^3+3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2+\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
\left.+\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_3(z)=0
\end{multline}

Let us first study equation \eqref{w1}: its Borel transform is

\begin{multline*}
-\zeta^3\tilde{w}_1+\zeta\tilde{w}_1-(1-2p)\int_0^\zeta\tilde{w}_1(t)t^2dt+\frac{(17-30p+12p^2)}{9}\int_0^\zeta(-t\tilde{w}_1(t))(\zeta-t)dt+\\
+\frac{8}{27}(p^3-6p^2+11p-6)\int_0^\zeta\tilde{w}_1(t)\frac{(\zeta-t)^2}{2}dt=0
\end{multline*}

@@

\begin{multline*}
\left(\zeta-\zeta^3\right)\tilde{w}_1^{(3)}(\zeta)+\left(3-2(5-p)\zeta^2\right)\tilde{w}_1''(\zeta)-\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\zeta\tilde{w}_1'(\zeta)+\\
+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\tilde{w}_1(\zeta)=0
\end{multline*}

we set $y=\zeta^2$

%\begin{multline}
%\left[-4y(y-1)(2y\partial_y^3+3\partial_y^2)+3(4y\partial_y^2+2\partial_y)-2(5-p)y(4y\partial_y^2+2\partial_y)+\right.\\
%\left.-2y\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\partial_y+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\right]\tilde{w}_1(y)=0
%\end{multline}
\begin{multline}\label{eq:hw1}
y^2(1-y)\tilde{w}_1^{(3)}(y)+y\left((p-\frac{13}{2})y+3\right)\tilde{w}_1''(y)-\left(y\left(\frac{305}{36}-\frac{10}{3}p+\frac{p^2}{3}\right)-\frac{3}{4}\right)\tilde{w}_1'(y)+\\
+\frac{1}{27}\left(p-\frac{5}{2}\right)\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\tilde{w}_1(y)=0
\end{multline}

@@

therefore, $\tilde{w}_1(y)=c_1\,\,{}_3F_2\left(\mathbf{a}_0;\mathbf{b}_0;y\right)$.

@@

\begin{multline}
-\zeta^3\tilde{w}_2(\zeta)-3\zeta^2\tilde{w}_2(\zeta)-2\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt-(1-2p)\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
+\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
-\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
-\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
\end{multline}

@@

\begin{multline}
\left[\left(\zeta^3+3\zeta^2+2\zeta\right)\partial_\zeta^3 +6\partial_\zeta^2+\left(p-\frac{17}{2}\right)\zeta\left(\zeta+\frac{1}{2}\right)\partial_\zeta^2+\right.\\
\left. \left(\frac{p^2}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(\zeta+1\right)\partial_\zeta+\frac{1}{27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(\zeta)=0
\end{multline}

@@

\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} R_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
where $R_k$ has degree $n-k$. \textcolor{gray}{has to be done}

@@

The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
which seem analogous to the trans-monomials above. Borel summation makes the analogy precise. We will see in Section~\ref{bessel-regularity} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$. This is an evidence of Theorem~\ref{thm:1}.
